Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex

% \linespread{1.1}
\begin{table}[h]
	\begin{tabular}{|c|c|cccc|}
	\cline{1-6}
	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	\end{tabular}
	\caption{Encoding for the Intro Example}
	\label{tab:assemble-example-encoding}
\end{table}
% \linespread{1.0}

@@

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline

	\end{tabular}
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
\end{table}

Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
As a result, each classifer only has $10\%$ parameters of the original full network.

@@

We train each classifer with $1500$ iterations with a batch size $200$. 
The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
We only train the pruned model i.e. weights of the pruned channels will remain zero.
After finetune, most of the classifers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
\paragraph{Fusion} We implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers. 
Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers are shown in \cref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
	\hline
	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\end{tabular}
    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
\end{table}

@@

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	& class-0 & class-1 & class-2 & class-3 & class-4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 &\\
	\hline
	\end{tabular}
    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
\end{table}

>>>>

% \linespread{1.1}
\begin{figure}[h]
	\begin{tabular}{|c|c|cccc|}
	\cline{1-6}
	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	\end{tabular}
	\caption{Encoding for the Intro Example}
	\label{fig:assemble-example-encoding}
\end{figure}
% \linespread{1.0}

@@

\begin{table}[h]
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline
	\end{tabular}
\end{table}

Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $pr$ i.e. if $pr=0.9$, $90\%$ of channels in all layers are pruned. 
As a result, each classifer only has $10\%$ parameters of the original full network.

@@

We train each classifer with $1500$ iterations with a batch size $200$. 
The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
We only train the pruned model i.e. weights of the pruned channels will remain zero.
With a prune ratio $pr\leq0.9$, most of the classifers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
In this section, we implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers. According to the 0/1 result of each classifer, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.

\paragraph{Fusion}We implement \cref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this \cref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers with different prune ratio is shown in \cref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[h]

    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Classifier ID & 3 & 4 & 1 & 2 \\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
	\hline
	\end{tabular}
\end{table}

@@

\begin{table}[h]

    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline

	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\

	\hline
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\

	\hline

	\end{tabular}
\end{table}

From \cref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network. 
When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency. When $pr=0.9$, we can inference with the $4$ classifiers in parallel, which can save about $90\%$ computing consumption on a single device.
